### 2021-07-16 doc/thesis/chapters/implementation.tex
testing strategies

%%%%%%%%%%%%%
\subsubsection{General}

@@

%%%%%%%%%%%%%
\subsubsection{Framework cocotb}
\label{sub:FrameworkCocotb}

@@

%%%%%%%%%%%%%
\subsection{Testbench Architecture}

@@

Fig.\ref{fig:bd_testbench_architecture_vhdl} shows a block diagram of the implemented architecture.
The split between the Python environment and the VHDL implementation is clearly visible but is represented from the developers perspective.
The actual interfaces, as described in \ref{sub:FrameworkCocotb}, are hidden to maintain the overview of the implemented architecture.\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Channel Selection (IF to Channel-BB)}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Phase Detector}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{other Elements}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Channel Selection (IF to Channel-BB)}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Phase Detector}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{other Elements}

>>>>

%%%%%%%%%%%%%
\subsubsection{General}
\label{sub:VHDL:Testbench:General}

@@

%%%%%%%%%%%%%
\subsubsection{Framework cocotb}
\label{sub:VHDL:FrameworkCocotb}

@@

%%%%%%%%%%%%%
\subsection{Testbench Architecture}
\label{sub:VHDL:TestbenchArchitecture}

@@

Fig.\ref{fig:bd_testbench_architecture_vhdl} shows a block diagram of the implemented architecture.
The split between the Python environment and the VHDL implementation is clearly visible but is represented from the developers perspective.
The actual simulator interfaces, as described in \ref{sub:VHDL:FrameworkCocotb}, are hidden to maintain the overview of the implemented architecture.\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Testing Strategies}

Common strategies for testing are unit tests and integration tests, which represent different levels of testing.
Unit tests specifically target a single unit, while integration tests verify the combination of multiple units as a whole.
Both of these stragegies are important.
Given all unit tests being successful, it is ensured that all these single units are implemented correctly.
However, their combination and interaction may still be subject to error - this is where integration tests unfold their potential.
Implementation errors in the glue logic between the units, as well as the interaction of the respective interfaces can be found in these integration tests.

The testbench architecture presented above represents an integration test, since the DUT is tested as an entire block.
The advantage thereof is, that it tests the DUT in the same way as it will be integrated within the target hardware, the FPGA.
However, in case the DUT fails to produce a correct output in the integration test, it is not always visible where exactly the error is located.
Thus, in addition to the DUTs' interfaces, additional signals are logged from the inside of the DUT. that can be accessed through the testbench. white box: disadvantage: test needs to change as well, when implementation changes
--> white box, black box

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Unit Tests}
FIR the only unit that is worth the effort (others are only delays, and additions/substractions respectively)

A unit test only targets a single unit of the system, as the name already describes.
This is in the contrary to an integration test, which tests the combination of several units into an integrated system.
The testbench architecture that is developed in \ref{sub:VHDL:TestbenchArchitecture} represents such an integration test.
However, if an integration test fails, it is not always

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{TODO: Other Stuff...}

@@

The implemented testbench structure, as well as some specific implementation details are explained here.

@@

A testbench is equally important in the HLS implementation, as it is for the VHDL implementation, explained in \ref{sub:VHDL:Testbench:General}.
The testbench simulation is

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{TODO: Other Stuff...}
